---
title: "Assignment2 - Plotting"
author: "Ethan T. Schmidt"
date: "September 17, 2018"
output: 
    html_document: 
        number_sections: yes
        self_containted: yes
        css: solarized_dark.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This homework involves plotting and data manipulation. It requires the use of two new datasets, starwars and flights which live in the dplyr and nycflights13 packages respectively.
```{r, message=FALSE}
library(dplyr)
library(ggplot2)
theme_solarized_dark <- function() {
    theme_dark() +
        theme(
            plot.background = element_rect(fill = "#073642"), 
            axis.text = element_text(color = '#eee8d5'), 
            text = element_text(color = '#eee8d5'))
}
```

# Load the starwars dataset from the dplyr package. Create a scatter plot of characters' heights (x-axis) against their masses (y-axis). Be sure to label the axes and give the graph a title.
```{r}
data(starwars)
starwars
ggplot(starwars, aes(x=height, y=mass)) +
    geom_point() +
    ggtitle('Characters\' Heights vs Mass') +
    theme_solarized_dark()
```
# Create a histogram of birth year of starwars characters' birth year.
```{r}

ggplot(starwars, aes(x=birth_year)) +
    geom_histogram(binwidth = 10) +
    theme_solarized_dark()
```
# Create density plots of heights faceted by gender. Change the ﬁll to something other than the default color, and use the theme theme_bw(). Be sure to let y-axis scales vary by gender.
# Create a violin plot of characters' heights if they are of species type “Human”, “Droid”, “Wookiee”, or “Yoda’s species”. Use the economist theme in the ggthemes package.
# Use the contains function to select columns from the flights dataset in the nycflights13 package, that contain the word "dep". Use starts_with to select columns that start with the letter "S". Read Chapter 12 if you are uncertain about these functions.
# Calculate the mean and standard deviation of dep_delay, arr_delay, air_time and distance, for each origin, in the flights dataset. Be sure to account for missing (NA) values. Chapter 4 discusses ways to deal with NAs.
# Use filter to return rows from the flights dataset that originate in JFK and depart in the afternoon.
# Create a new column in the flights dataset showing the average speed, calculated as distance divided by air_time. Name the column "AvgSpeed". Use this column to calculate the average speed for flights departing each of the NYC airports.