---
title: "Assignment 4"
output: 
    html_document: 
        number_sections: yes
        self_containted: yes
        css: solarized_dark.css
---

```{r settings,echo=FALSE}
knitr::opts_chunk$set(message=FALSE,cache=TRUE,error=TRUE)
```

# Read the NYC Pluto data about land value from in Manhattan from https://query.data.world/s/WuYif0WbZCxzOLjLh95TY9rK--Tw64 (Links to an external site.)Links to an external site.. Ignore any warnings caused by using read_csv if you use that function. The data contain characteristic information about individual lots in Manhattan. We want to model the value of lots (TotalValue) as a function of its characteristics.
```{r}
# land data set
land <- readRDS(here::here('data', 'manhattan_Train.rds'))
```


## First, generate summary statistics of variables you find interesting and build plots to help you explore the data. Choose the type of plot that makes the most sense to you.
```{r}
# choosing variable for model
land1 <- lm(TotalValue ~ LotArea + NumFloors + ZoneDist1 + PolicePrct + Built + Class, data=land)
summary(land1)
```
```{r}
library(ggplot2)
library(ggthemes)
theme_solarized_dark <- function() {
    theme_dark() +
        theme(
            plot.background = element_rect(fill = "#073642"), 
            axis.text = element_text(color = '#eee8d5'), 
            text = element_text(color = '#eee8d5'))
}

# plot x and y
ggplot(land1, aes(x=LotArea, y=TotalValue)) +
        geom_point() +
        scale_x_log10(labels = scales::comma) +
        theme_solarized_dark()
```

## Next, regress TotalValue against FireService, LotArea, LotFront and HistoricDistrict. Visualize with a coefficient plot and interpret each coeﬃcient in your own words.
```{r}
land2 <- lm(TotalValue ~ FireService + LotArea + LotFront + HistoricDistrict, data=land)
summary(land2)
```
```{r}
# The value of the property goes down quite a bit if near a fire station, even more so if near a fire squad unit
# Value increases with both lot size and fascade size, as well as if in a Historic District, although not as much
```

# Continue modeling the Pluto data until the BIC of the model is below 1,040,000. Show a coefficient plot of the final model. Then display a coefficient plot, with multiplot, showing both the previous model and this model.
```{r}
BIC(land1, land2)
```
```{r}
# Got it good on first try!
# graph it
library(coefplot)
multiplot(land1, land2, sort='magnitude')
```

# Load the orings dataset from the DAAG package. The dataset contains information on characteristics of space shuttle launches in the early 1980s, and the number and type of 45 O-ring failures. Investigate whether the temperature at launch has an impact on the probability of O-ring failure using binary (logistic) regression.
```{r}
install.packages('DAAG')
data(orings, package='DAAG')
```

## First, use mutate (or some other method) to create a binary variable indicating whether there is any erosion (Erosion) or blow-by (Blowby).
```{r}
library(dplyr)
orings1 <- orings %>%
    mutate(EorB=ifelse(Blowby > 0 | Erosion > 0, TRUE, FALSE))
head(orings1)
```
## Next, train a binary regression where this new variable is the response and Temperature is a predictor. Does Temperature impact the risk of o-ring failure?
```{r}
orings2 <- glm(EorB ~ Temperature, 
               data=orings1, 
               family=binomial)
summary(orings2)
```
```{r}
# The colder it gets, the greater the risk of O-ring failure
```
# Load the DoctorAUS dataset from the Ecdat package. Use Poisson regression to model the number of doctor visits (doctorco). 
## Report the BIC and display a coefficient plot on the original scale by setting the trans argument of coefplot to the appropriate inverse function. This requires reading section 20.2.
```{r}
data(DoctorAUS, package='Ecdat')
DoctorAUS1 <- glm(doctorco ~ sex + age + income + insurance + illness, 
                 family='poisson', data=DoctorAUS)
BIC(DoctorAUS1)
```
```{r}
coefplot(DoctorAUS1, trans=invlogit)
```

## Model the number of doctor visits again and account for overdispersion by using a quasipoisson family. Report the overdispersion parameter and display a multiplot of the previous model and this one.
```{r}
DoctorAUS2 <- glm(doctorco ~ sex + age + income + insurance + illness, 
                 family='quasipoisson', data=DoctorAUS)
multiplot(DoctorAUS1, DoctorAUS2)
```

