---
title: Assignment 1 - R Bascics
author: Ethan T. Schmidt
date: September 7, 2018
output: 
    html_document: 
        number_sections: yes
        self_containted: yes
        css: solarized_dark.css
---

```{r settings,echo=FALSE}
knitr::opts_chunk$set(message=FALSE,cache=TRUE,error=TRUE)
```

# Variable Types
## What are the four main types of variables?
```{r}
class(20.3)
class(FALSE)
class("zebra")
date <- as.Date("2018-09-10")
class(date)
```
## What are two functions that can be used to determine a variable type?
```{r}
x <- 45
class(x)
is.numeric(x)
```

# Vectors
## Create a vector of numbers from one to ten called numVec. 
```{r}
numVec <- 1:10
numVec
```
## Use the sum function to calculate the sum of this vector.
```{r}
sum(numVec)
```

# Functions
## Write a function that has two arguments. If the first argument is bigger, return the sum of the numbers. If the second argument is bigger, return the product of the numbers.

# CSV
## What data type does read_csv return?

# Excel
## What data type does read_excel return?

# Importing Data
## Read the acs_ny.csv data from https://jaredlander.com/data/Links to an external site.
## Display for the first 10 rows and the last 10 rows.