---
title: "CAO Sales Data"
author: "Ethan T. Schmidt"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First, identify which product has had the highest revenue growth rate over the last 4 years, and outline major contributing factors to that growth. 

Read in Excel Data
```{r}
library(readxl)
salesXL <- read_excel('IBM_CAO.xlsx', sheet=3)
head(salesXL)
```
## Find Revenue per Client
```{r}
library(dplyr)
salesXL$DATE <- year(as.Date(salesXL$DATE, "%d/%m/Y%", tz="GMT"))
salesXL <- salesXL %>% mutate(Client_Rev = NUM_LICENSE*PRICE_PER_LICENSE)

head(salesXL) %>% 
    select(DATE, CLIENT_ID, PRODUCT, NUM_LICENSE, PRICE_PER_LICENSE, Client_Rev)
```
## Group Revenue Growth by Product
```{r}
salesXL %>% select(DATE, PRODUCT, Client_Rev) %>%
    spread(key=DATE, value = Client_Rev)
```



## Then, provide your recommendations for how to grow overall revenue. Please use the data attached to provide rationale for your recommendations.


