---
title: "Earn.org Test"
author: "Ethan T. Schmidt"
date: "May 20, 2019"
output: 
    html_document:
        toc: true
---
```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
#load data & packages
library(dplyr)

salaries <- read.csv('salary_data.csv')
head(salaries)
```
# Which departments have the highest and lowest average salaries?
```{r}
#convert salary data type 
salaries$salary <- as.numeric(substring(salaries$salary, 2))

#group by department
avgs <- salaries %>% 
        group_by(department) %>% 
        summarize(avg_sal=mean(salary)) %>% 
        arrange(desc(avg_sal))

#highest average salary
filter(avgs, row_number()==1)
#lowest avaerage salary
filter(avgs, row_number()==n())
```
# How many different job titles are there that are held by at least 10 people?
```{r}
#group by job_title
titles <- salaries %>% 
        group_by(job_title) %>%
        add_count() %>% 
        filter(n>=10)

count(titles)
```
# Of those job titles held by at least 10 people, which one has the highest median salary?
```{r}
titles <- titles %>% 
        summarize(median=median(salary)) %>% 
        arrange(desc(median))

head(titles, 2)
```
# How many people have the word "Engineer" in their job title.
```{r}

```

# Of the people who with "Engineer" in their Job, what percentage of them are Civil Engineers?

# How many people joined the Fire Department in 2000 between July 1st and September 15th?
