---
title: "Earn.org Test"
author: "Ethan T. Schmidt"
date: "May 20, 2019"
output: 
    html_document:
        toc: true
---
```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
#load data & packages
library(dplyr)

salaries <- read.csv('salary_data.csv')
head(salaries)
```
# Which departments have the highest and lowest average salaries?
```{r}
#convert salary data type 
salaries$salary <- as.numeric(substring(salaries$salary, 2))

#group by department
avgs <- salaries %>% 
        group_by(department) %>% 
        summarize(avg_sal=mean(salary)) %>% 
        arrange(desc(avg_sal))

#highest average salary
filter(avgs, row_number()==1)
#lowest avaerage salary
filter(avgs, row_number()==n())
```
# How many different job titles are there that are held by at least 10 people?
```{r}
#group by job_title
titles <- salaries %>% 
        group_by(job_title) %>%
        add_count() %>% 
        filter(n>=10) 

titles2 <- titles %>% 
        summarize(count=n())

cat('Number of different job titles are there that are held by at least 10 people: ', length(titles2$count))
```
# Of those job titles held by at least 10 people, which one has the highest median salary?
```{r}
titles <- titles %>% 
        summarize(median=median(salary)) %>% 
        arrange(desc(median))

head(titles, 2)
```
# How many people have the word "Engineer" in their job title.
```{r}
#easy, quick way to get count that matches string

cat('Number of engineers: ', length(grep('ENGINEER', salaries$job_title)))
```
# Of the people who with "Engineer" in their Job, what percentage of them are Civil Engineers?
```{r}
#more useful way of getting values
engineers <- salaries %>% 
            filter(grepl('ENGINEER', job_title))

civils <- engineers %>% 
        filter(grepl('CIVIL ENGINEER', job_title))

cat('Percentage of engineers who are civil engineers: %', first(count(civils)/count(engineers)*100))
```
# How many people joined the Fire Department in 2000 between July 1st and September 15th?
```{r}
#convert date types
salaries$Join.Date <- as.Date(salaries$Join.Date)

#filter by department and date
firedept <- salaries %>% 
        filter(department=='FIRE') %>% 
        filter(Join.Date>='2000-06-01' & Join.Date>='2000-09-15')

cat('Number of people joined the Fire Department in 2000 between July 1st and September 15th: ', first(count(firedept)))
```

