---
title: 'Pricing #1'
author: "Ethan T. Schmidt"
date: "March 31, 2019"
output: 
    html_document: 
        toc: yes
       # css: solarized_dark.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What are the benefits fo the new pile pads?

The new pads are more durable, meaning that they need to be replaced less frequently, and are more efficient, meaning that they dissapate heat more effectively and cause the pile to crack less. Additionally, the manufacturing process allows for any diameter pad to be made form the same strip of metal.

## EVC of a new pile pad

```{r}
#Total time saved IAW Kendrick test

df <- data.frame("name" = c("Conv", "CMI"), "feet_driven" = c(150, 200), "piles_per_set" = c(15, 300), "pads_per_set"= c(24, 6), "sets_required" = c(20, 1), "set_changes" = c(20, 1), "time_per_change"= c(20, 4), "cost_per_set" = c(150, 0))

df["total_change_time"] <- df$set_changes * df$time_per_change

total_feet_needed <- 15000

df['total_drive_time'] <- total_feet_needed / df$feet_drive 
df['total_time'] <- (df$total_change_time / 60) + df$total_drive_time

time_saved <- df$total_time[1] - df$total_time[2]

cat('Time saved: ', time_saved)

#Time savings in dollars
df["total_pads_needed"] <- df$sets_required * df$pads_per_set
cost_per_hour <- sum(102, 156, 24, 63, 30, 39) #excluding overhead

own_equp <- .75
value_of_time_saving <- time_saved * cost_per_hour
```

```{r}
#EVC 

df['cost_of_time'] <- df$total_time * cost_per_hour

conv_cost_pads <- 150 * 20

conv_total_cost <- df$cost_of_time[1] + conv_cost_pads

CMI_set_cost <- conv_total_cost - df$cost_of_time[2]

CMI_pad_cost <- CMI_set_cost / df$pads_per_set[2]

cat('Pad Coast: ', CMI_pad_cost)
```
```{r}
#Costs to produce

manufacture_costs <- 207.54

sugg_margin <- .5
retail_margin <- .4

sugg_price <- manufacture_costs * (1 / sugg_margin) * (1.4)
```

## Price set for smallest pads

If the total cost of a new pad is $207.54 and the EVC of the new pad to the consumer is $607.2, CMI should charge at least $600 per single pad, with price braks for larger quantities; this saves all the comsumers at least some money, while justifying the overhead allocation costs to re-tooling the new pads. 
```{r}
# Additional Capacity
mkt_feet_year <- mean(290000000, 390000000)
feet_per_set <- 10000
sets_needed <- mkt_feet_year/feet_per_set
pads_per_set <- 6
pads_needed <- sets_needed/pads_per_set
cat("Total Market Size in Pads:",pads_needed)
capacity_needed_month <- pads_needed/12
cat("Total Capacity per Month:",capacity_needed_month)
```
Although the market might need new pads, CMI will have a hard time convincing them; hwever, if they do, CMI will be able to command a very large market share. I recommend that CMI not purchase any additional capacity until they eceed a 50% market share and are continueing to grow.

Key influencers to target would be the _Construction Engineers_ and the _Independent contractors_ becasue botht hese groups ae knowledgeable enough about the industry to recognize the importance of the new pads and neither have a conflicting interest in keeping construction times higher or more piles used.